The \dealii Library, Version 9.2

### 2020-05-28 9.2/paper.tex
Inline a figure.
Typos and support

Previously, all triangulation classes of \texttt{deal.II} had in common that the coarse grid is replicated by
all processes in a parallel environment, and the actual mesh used for computations is constructed by repeated
refinement. However, this has its limitations in industrial
applications, where frequently the mesh comes
from an external mesh generator in the form of a file that already contains millions
or tens of millions of cells. For such configurations, applications might exhaust
available memory already while reading the mesh on each MPI process.

@@

For this release, the most noteworthy improvements for the GPU support are the
simplification of the kernel written by user, improvement of the error messages,
and overlapping of computation and communication when using CUDA-aware MPI with
the matrix-free framework. In order to simplify user code, we know recompute the
local degree of freedom and quadrature point indices instead of having the user
keeping track of them. A new option to overlap computation and communication is
now available when using CUDA-aware MPI and matrix-free. The underlying idea is
that only the degrees of freedom (dofs) on the boundary of the local domain
require communication. Before evaluating the matrix-free operator at these
degrees of freedom, we need to communicate the ghosted dofs from other
processors.  Similarly once the operator has been evaluated, we need to update
the resulting global vector with values from other processors. The strategy that
we are using consist in splitting the dofs in three groups: one group of dofs
that are on the local boundary and two groups each owning half of the interior
dofs. When evaluating the matrix-free operator, we start the MPI communication
to get the ghosted dofs and evaluate the operator on one of the two interior
dofs group. When the evaluation is done, we wait for the MPI to be over and
then, evaluate the operator on the boundary dofs group. When this evaluation is
over, we start the communication to update the global vector, we evaluate the
operator on the last of group of dofs, and finally wait for the MPI
communication to finish.

@@

>>>>

Previously, all triangulation classes of \texttt{deal.II} had in common that the coarse grid is replicated by
all processes in a parallel environment, and the actual mesh used for computations is constructed by repeated
refinement. However, this has its limitations in
applications where the mesh comes
from an external mesh generator in the form of a file that already contains millions
or tens of millions of cells. For such configurations, applications might exhaust
available memory already while reading the mesh on each MPI process.

@@

For this release, the most noteworthy improvements for the GPU support are the
simplification of the kernel written by user, improvement of the error messages,
and overlapping of computation and communication when using CUDA-aware MPI with
the matrix-free framework. In order to simplify user code, we now recompute the
local degree of freedom and quadrature point indices instead of having the user
keeping track of them. A new option to overlap computation and communication is
now available when using CUDA-aware MPI and matrix-free. The underlying idea is
that only the degrees of freedom (dofs) on the boundary of the local domain
require communication. Before evaluating the matrix-free operator at these
degrees of freedom, we need to communicate the ghosted dofs from other
processors.  Similarly once the operator has been evaluated, we need to update
the resulting global vector with values from other processors. The strategy that
we are using consist in splitting the dofs in three groups: one group of dofs
that are on the local boundary and two groups each owning half of the interior
dofs. When evaluating the matrix-free operator, we start the MPI communication
to get the ghosted dofs and evaluate the operator on one of the two interior
dofs group. When the evaluation is done, we wait for the MPI to be over and
then, evaluate the operator on the boundary dofs group. When this evaluation is
over, we start the communication to update the global vector, we evaluate the
operator on the last of group of dofs, and finally wait for the MPI
communication to finish.

@@

A.~V.~Grayver was partially supported by the European Space Agency Swarm DISC program.
